\section{Contributions to the Paper}
\begin{itemize}
\item The proof of distinction\_implies\_winning\_budgets in \ref{deviation:lemma1_Q_a} 
(lemma 1 in \cite{bisping2023lineartimebranchingtime}) required ammending, the sixt case
of the inductiv property is ammended by $Q_\alpha \neq {}$, in order to be able to directly
apply the induction hypothesis in the proof.

\item The sixth inductive property of the lemma strategy\_formulas\_distinguish in \ref{deviation:lemma3} 
(lemma 3 in \cite{bisping2023lineartimebranchingtime}) was adjusted.
The case of $g=(p,\alpha ,p', Q- Q_\alpha, Q_\alpha)_d^\eta$ being a defender branching position
required adding the assumtions that $p \overset{\alpha}{\longrightarrow} p'$ and $Q_\alpha \neq \emptyset$
to match those of the branching conjunction move rule (cf. \cite[p. 13]{bisping2023lineartimebranchingtime}). 

\item In the definition of the weak spectroscopy game in section \ref{specmoves} the moves were changed: 
The move `finishing' was removed. This move adjusted the cost of an empty immediate conjunction to be zero.
This is inconsistent with the definition of the expressiveness price. This move is also not needed, as in the case of $Q$ being an empty set at an attacker immediate position, the attacker can move to the corresponding
defender conjunction position by performing a `delay' move, followed by a `late instable conjunction' move. Both of these moves have zero costs.

\item The move empty\_stbl\_conj\_answer (moving from adefender stable conjunction position to a defender conjunction
position if $Q$ is empty) with costs $e_4$ was added. This is necessary for the proof of lemma 
winning\_budget\_implies\_strategy\_formula in section \ref{derivation:lemma3}. Before 
$e \in Win_a (p, \emptyset)_d^s $ was true for any energy (not equal to the defender\_win\_level), in particular $\bold{0}$. 
Since an empty stable conjuction has costs of $e_4$ no strategy formula with an appropriate price could be constructed. 
With the added move $e_4 \leq e $ holds true for any $e \in Win_a (p, \emptyset)_d^s $ and therefore resolves this issue.

\item The changes of the weak sprectroscopy game impact the derivation of strategy formulas. As shown in the proof 
of lemma winning\_budget\_implies\_strategy\_formula in section \ref{derivation:lemma3} our definition that is close 
to the paper still works. (For example one could choose to add a derivation rule corresponding to the move empty\_stbl\_conj\_answer to the definition 
of strategy formulas. We instead constructed the necessary formula in the proof and used that for an empty set the rule stable\_conj could be applied.
More detail is found in the proof in the case $Q=\emptyset$ in case 5 ($g$ being a defender stable conjunction position) 
of case 3 ($g$ being a defender position with successors).)
\item In lemma strategy\_formulas\_distinguish in Section \ref{derivation:lemma3} the case of $g$ being a defender branching position was adjusted: 
When considering $g=(p,\alpha ,p', Q- Q \alpha, Q \alpha)_d^\eta$ the conditions $p \overset{\alpha}{\longrightarrow} p'$ and $Q \alpha \neq \emptyset$ were 
added. 
\end{itemize}
\item In lemma strategy\_formulas\_distinguish in section \ref{derivation:lemma3} the case of $g$ being a defender branching position was adjusted: 
When considering $g=(p,\alpha ,p', Q- Q \alpha, Q \alpha)_d^\eta$ the conditions $p \overset{\alpha}{\longrightarrow} p'$ and $Q \alpha \neq \emptyset$ were added. 
\end{itemize}
